---
title: "615 Final Report - Interactive Stock Charts"
author: "Matthew Zebert"
date: "December 15, 2017"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
```


## Long term Goal:

The long term goal of this project is to create an shiny app that can display a myriad of statistical tests and model outputs for the future of a stock price prediction model. This model is currently being developed (684 Final), and utlizes stock price history, volume, market capitalization, and market sentiment to attempt a prediction of the future of the stock.

## Short term Goal:

As I am new to Shiny or any HTML work, the short term goal, and the goal of this project is to create and simple version of an interactive stock chart. With this project as a working first model, I can continue to scale up it's interactive options, tests, visualizations, and other outputs of the long term model goal

## What does this Shiny app - "Interactive Stock Charts" - do?

This app utlizes the r package quantmod in order to pull stock data from free online financial data API's. With this data, the app allows the user to interactivly display the price and volume for varies date ranges and chart options.


## List of Companies

```{r, include=FALSE}
Stock <- c("Apple", "Microsoft", "Amazon", "Google", "Intel", "IBM", "Oracle", "Tesla", "Electronic Arts", "Facebook")
Ticker <- c("APPL", "MSFT", "AMZN", "GOOGL", "INTC", "IBM", "ORCL", "TSLA", "EA", "FB")

df <- data.frame(Stock,Ticker)
```

```{r, echo=FALSE}
kable(df)
```

 
## Link to the Shiny app online:

https://mzebear.shinyapps.io/Interactice_Stock_Chart_615/
